---
title: "HW-03 - J Stewart"
output: html_document
---

```{r allow errors, echo = FALSE}
knitr::opts_chunk$set(error = TRUE)
```


```{r}
library(gapminder)
library(tidyverse)
```

## GitHub Pages (6%) NEW
From now on, whenever you produce an HTML file output, you are expected to make it viewable as a webpage – for example, through GitHub Pages. There are / will be instructions added to the assignments home page on how to do this with GitHub Pages.

You should also provide links to these HTML pages in an easy-to-find location, and use words to describe what the link brings you to – probably in a README.md file in your hw03 folder
Pick three of the six tasks below, and produce:

a tibble, using dplyr as your data manipulation tool;
an accompanying plot of data from the tibble, using ggplot2 as your visualization tool; and
some dialogue about what your tables/figures show (doesn’t have to be much).


Task Option 1
Report the absolute and/or relative abundance of countries with low life expectancy over time by continent: Compute some measure of worldwide life expectancy – you decide – a mean or median or some other quantile or perhaps your current age. Then determine how many countries on each continent have a life expectancy less than this benchmark, for each year.




```{r}
summary(gapminder)
```

##Task Option 2
*Maximum and minimum of GDP per capita for all continents.*
```{r}
gapminder %>%
  group_by(continent) %>%
  summarise (min_gdpPercap = min(gdpPercap),
            max_gdpPercap = max(gdpPercap))
```

*Boxplot of GDP per capita for all continents.*
```{r}
ggplot(gapminder, aes(continent, gdpPercap)) +
  geom_boxplot()
```


##Task Option 3
**Spread of GDP per capita within the continents.**

```{r}
gapminder %>%
  group_by(continent) %>%
  summarise (Ave_gdpPercap = mean(gdpPercap))  
```
**Density plot of GDP per Capita by continent**
```{r}
ggplot(gapminder, aes(gdpPercap, continent)) +
  ggridges::geom_density_ridges()
```






