---
title: "HW-04"
output: html_document
---

```{r allow errors, echo = FALSE}
knitr::opts_chunk$set(error = TRUE)
```


```{r}
library(gapminder)
library(tidyverse)
```

Exercise 1: Univariate Data Reshaping (30%)
Choose *EITHER* “Univariate Option 1” or “Univariate Option 2”. Both of these problems have three components:

Putting data in wider format;
5%: Did you produce the correct result?
5%: Code quality
Producing a plot of the wide data; (10%)
5%: Did you produce a sensible visualization?
5%: Code quality
Re-lengthening the wider data. (10%)
5%: Did you produce the correct result?
5%: Code quality
You are expected to use pivot_wider() and pivot_longer() for reshaping, and ggplot2 for the plot.

Regarding the plot:

Don’t worry about plotting all of the data from the wide tibble.
The plot should be something that someone might actually want to produce in an analysis.
Univariate Option 1
Make a tibble with one row per year, and columns for life expectancy for two or more countries.
Take advantage of this new data shape to scatterplot life expectancy for one country against that of another.
Re-lengthen the data.