---
title: "HW-04"
output: html_document
---
```{r allow errors, echo = FALSE}
knitr::opts_chunk$set(error = TRUE)
```
```{r}
library(gapminder)
library(tidyverse)
```

##Exercise 1: Univariate Data Reshaping
**Univariate Option 1**
*Make a tibble with one row per year, and columns for life expectancy for Japan and Rwanda.*
```{r}
Japan_Rwanda <- as.tibble(gapminder) %>%
  group_by(year) %>%
  filter(country %in% c("Japan", "Rwanda")) %>%
  select(year, country, lifeExp)
```

```{r}
view(Japan_Rwanda)
```

```{r}
Japan_Rwanda_wide <- Japan_Rwanda %>%
    pivot_wider(names_from = "country", values_from = "lifeExp")
```

```{r}
view(Japan_Rwanda_wide)
```

```{r}
Japan_Rwanda_wide %>%
  rename(Japan_lifeExp = Japan) %>%
  rename(Rwanda_lifeExp = Rwanda)
```

*Scatterplot life expectancy for Japan against Rwanda.*
```{r}
Japan_Rwanda %>%
  ggplot(aes(year, lifeExp)) + 
    geom_line(aes(group = country), colour = "grey50") + 
    geom_point(aes(colour = country))
```

*Re-lengthen the data.*
```{r}
Japan_Rwanda_long <- Japan_Rwanda_wide %>%
    pivot_longer(cols = c("Japan","Rwanda"), names_to = "country", values_to = "LifeExp")
```

```{r}
Japan_Rwanda_long
```

##Exercise 2: Multivariate Data Reshaping (30%)
**Multivariate Option 1**

*Make a tibble with one row per year, and columns for life expectancy and GDP per capita for Japan and Rwanda.*
```{r}
Japan_Rwanda_GDP <- as.tibble(gapminder) %>%
group_by(year) %>%
  filter(country %in% c("Japan", "Rwanda")) %>%
  select(year, country, gdpPercap)
```

```{r}
view(Japan_Rwanda_GDP)
```

```{r}
Japan_Rwanda_GDP_wide <- Japan_Rwanda_GDP %>%
    pivot_wider(names_from = "country", values_from = "gdpPercap")
```

```{r}
view(Japan_Rwanda_GDP_wide)
```

```{r}
Japan_Rwanda_GDP_wide %>%
  rename(Japan_GDP = Japan) %>%
  rename(Rwanda_GDP = Rwanda)
```

```{r}
widest_Japan_Rwanda <- left_join(Japan_Rwanda_wide, Japan_Rwanda_GDP_wide, by = "year")
```

```{r}
view(widest_Japan_Rwanda)
```

**Re-lengthen the data.**

```{r}
Japan_Rwanda_long <- widest_Japan_Rwanda %>%
    pivot_longer(cols = c("Japan.x","Rwanda.x", "Japan.y", "Rwanda.y"), 
                 names_to = "country","LifeExp","gdpPercap")
```

##Exercise 3: Table Joins (30%)
*Read in the made-up wedding guestlist and email addresses using the following lines (go ahead and copy-paste these)*

```{r}
guest <- read_csv("https://raw.githubusercontent.com/STAT545-UBC/Classroom/master/data/wedding/attend.csv")
email <- read_csv("https://raw.githubusercontent.com/STAT545-UBC/Classroom/master/data/wedding/emails.csv")
```
**3.1 For each guest in the guestlist (guest tibble), add a column for email address, which can be found in the email tibble.**

```{r}
email_list <- rename(email, name = guest)
```

```{r}
view(email_list)
```

```{r}
guest_list_email <- left_join(guest, email_list, by = "name")

view(guest_list_email)
```


3.2 Who do we have emails for, yet are not on the guestlist?
```{r}
not_list <- guest_list_all %>%
  filter(party, is.na(TRUE))

view(not_list)
```


3.3 Make a guestlist that includes everyone we have emails for (in addition to those on the original guestlist).

```{r}
guest_list_all <- full_join(guest, email_list, by = "name")


view(guest_list_all)
```

