---
title: "Hw-05 J Stewart"
output: html_document
---

```{r allow errors, echo = FALSE}
knitr::opts_chunk$set(error = TRUE)
```
```{r}
library(gapminder)
library(tidyverse)
library(ggplot2)
library(ggridges)
```

## Exercise 1: Explain the value of the here::here package (10%)

Task: In your own words, summarize the value of the here::here package in 250 words or fewer.

### Why I should use the **here:here package
  
1. It will allow other people to open and run my code without changing the working drive.
2. It makes naming conventions easier. 
3. It will prevent Jenny from coming to my office to set my computer on fire.

## Exercise 2: Factor management (20%)

*Task: Choose one dataset (of your choice) and a variable to explore.*

*Ensure the variable you’re exploring is indeed a factor*
```{r}
class(gapminder$continent)
```

*Drop factor / levels*

```{r}
oceania_dropped <- gapminder %>% filter(continent != "Oceania")
```

```{r}
nlevels(gapminder$continent)
```

```{r}
oceania_dropped2 <- oceania_dropped %>% 
  droplevels()
```

```{r}
nlevels(oceania_dropped2$continent)
```

*Reorder levels based on knowledge from data*
```{r}
reorder <- oceania_dropped2 %>% 
  mutate(continent=fct_reorder(continent, lifeExp, min))
```

## Examine order of levels before and after change.
```{r}
(before <- levels(oceania_dropped2$continent))
```

```{r}
(after <- levels(reorder$continent))
```

```{r}
oceania_dropped2 %>% 
  arrange(continent)
```
```{r}
oceania_dropped2 %>% 
  ggplot(aes(x=lifeExp, y=continent, fill=continent)) +
  geom_density_ridges(alpha=0.6) +
  labs(title="Life Expectancy before Level-Reordering",
       x="Life Expectancy") +
  theme(legend.position="left")
```








```{r}
reorder %>% 
  ggplot(aes(x=lifeExp, y=continent, fill=continent)) +
  geom_density_ridges(alpha=0.6) +
  labs(title="Life Expectancy after Level-Reordering",
       x="Life Expectancy") +
  theme(legend.position="left")
```


## Exercise 3: File input/output (I/O) (20%)

Task: Experiment with write_csv()/read_csv()

```{r}
library(readxl)
```

```{r}
year_1977 <- gapminder %>%
  filter(year=='1977')
```

```{r}
year_1977
```



```{r}
# Write `year_1979` dataset to current directory:
write_csv(year_1977, here::here("1977_gapminder.csv"))
```

```{r}
# Read the dataset back in:
(reload_1977 <- read_csv(here::here("1977_gapminder.csv")))

```



```{r}
reload_1977$country <- factor(reload_1977$country)
reload_1977$continent <- factor(reload_1977$continent)
```

Play with factor levels and order your data with one of your factors.

```{r}
reload_1977 %>%
ggplot() +
  geom_col(aes(x = fct_reorder(continent, gdpPercap), y = lifeExp)) +
  theme_bw() +
  labs(x = "Continent", y = "Minimum life expectancy")
```


## Exercise 4: Visualization design (20%)

*From hw03* 
**Density plot of GDP per Capita by continent**
```{r}
ggplot(gapminder, aes(gdpPercap, continent)) +
  ggridges::geom_density_ridges()
```


```{r}
GDPperCap_by_Cont<- ggplot(gapminder, aes(gdpPercap, continent)) +
  ggridges::geom_density_ridges() +
  scale_x_continuous("GDP per Capita") +
  scale_y_discrete("Continent") +
  theme_minimal() + ggtitle("GDP per Capita by Continent")
```


## Exercise 5: Writing figures to file (10%)

*Task: Use ggsave() to explicitly save a plot to file. Include the exported plot as part of your repository and assignment.*

```{r}
GDPperCap_by_Cont <- "GDPperCap_by_Cont.png"
```

```{r}
plot_path <- here::here("hw05", "GDPperCap_by_Cont.png") 

```

```{r}
ggsave(GDPperCap_by_Cont)

```
